LAGOS lake depth

### 2020-02-26 tables/01_predictors.Rmd
create bathy specific predictor table

# pred_key <- read.csv("../data/predictor_key.csv", 
#                      stringsAsFactors = FALSE)
# 
# # scripts/02_aggregate_predictors.R
# dt_units <- readRDS("../data/dt_units.rds")

# cdl_vars <- readRDS("../data/dt.rds") %>%
#   dplyr::select(ag:wheat) %>%
#   summarize_all(median, na.rm = TRUE) %>%
#   tidyr::gather() %>%
#   dplyr::filter(value >= 1.4) %>%
#   arrange(desc(value)) %>%
#   pull(key)

# setwd("tables")
dt <- read.csv("../data/lagosus_depth_predictors.csv", 
               stringsAsFactors = FALSE) %>%
  distinct(lagoslakeid, .keep_all = TRUE) %>%
  dplyr::select(-contains("lagoslakeid"), 
                -contains("lake_nhd"), 
                -contains("lake_huc")) %>%
  tidyr::gather(key = "variable") %>%
  group_by(variable) %>%
  mutate(value = as.numeric(value)) %>%
  mutate(q10 = quantile(value, probs = c(0.1), na.rm = TRUE),
         q25 = quantile(value, probs = c(0.25), na.rm = TRUE),
         q50 = quantile(value, probs = c(0.5), na.rm = TRUE),
         q75 = quantile(value, probs = c(0.75), na.rm = TRUE),
         q90 = quantile(value, probs = c(0.9), na.rm = TRUE), 
         ratio = q90 / q10, 
         n = sum(!is.na(value), na.rm = TRUE)) %>%
  dplyr::filter(!is.na(q50)) %>%
  dplyr::distinct(signif(q10, 2), signif(q25, 2), signif(q50, 2), signif(q75, 2), signif(q90, 2), ratio, n) %>%
  dplyr::mutate_if(is.numeric, funs(as.character(signif(., 3)))) %>%
  dplyr::select(variable, 
         q10 = `signif(q10, 2)`,
         q25 = `signif(q25, 2)`,
         q50 = `signif(q50, 2)`,
         q75 = `signif(q75, 2)`,
         q90 = `signif(q90, 2)`,
         q10_q90_ratio = ratio,
         n)#  %>%
  # left_join(dt_units, by = "variable") %>%
  # dplyr::select(variable, units, everything())

@@

knitr::kable(dt, digits = 0, format = "markdown") 
#%>%
 # add_header_above(c(" ", " ", Ranges = 3, " ", " "))
```

>>>>

# setwd("tables")
nearshore <- read.csv("../data/00_geometry/nearshore.csv", 
                      stringsAsFactors = FALSE) %>%
  dplyr::select(llid, buffer_slope = slope_mean)
dt <- read.csv("../data/lagosus_depth_predictors.csv", 
               stringsAsFactors = FALSE) %>%
  distinct(lagoslakeid, .keep_all = TRUE) %>%
  left_join(nearshore, by = c("lagoslakeid" = "llid")) %>%
  dplyr::select(-contains("lagoslakeid"), 
                -contains("lake_nhd"), 
                -contains("lake_huc")) %>%
  tidyr::gather(key = "variable") %>%
  group_by(variable) %>%
  mutate(value = as.numeric(value)) %>%
  mutate(q10 = quantile(value, probs = c(0.1), na.rm = TRUE),
         q25 = quantile(value, probs = c(0.25), na.rm = TRUE),
         q50 = quantile(value, probs = c(0.5), na.rm = TRUE),
         q75 = quantile(value, probs = c(0.75), na.rm = TRUE),
         q90 = quantile(value, probs = c(0.9), na.rm = TRUE), 
         ratio = q90 / q10, 
         n = sum(!is.na(value), na.rm = TRUE)) %>%
  dplyr::filter(!is.na(q50)) %>%
  dplyr::distinct(signif(q10, 2), signif(q25, 2), signif(q50, 2), signif(q75, 2), signif(q90, 2), ratio, n) %>%
  dplyr::mutate_if(is.numeric, funs(as.character(signif(., 3)))) %>%
  dplyr::select(variable, 
         q10 = `signif(q10, 2)`,
         q25 = `signif(q25, 2)`,
         q50 = `signif(q50, 2)`,
         q75 = `signif(q75, 2)`,
         q90 = `signif(q90, 2)`,
         q10_q90_ratio = ratio,
         n)#  %>%
  # left_join(dt_units, by = "variable") %>%
  # dplyr::select(variable, units, everything())

@@

# knitr::kable(dt, digits = 0, format = "markdown") 
#%>%
 # add_header_above(c(" ", " ", Ranges = 3, " ", " "))
```

```{r predictors_table}
# setwd("figures")
dt <- dt %>%
  dplyr::filter(variable %in% 
              c("lake_meandepth_m", 
              names(readRDS("../data/01_depth_model/depth_training.rds")), 
              "buffer_slope")) %>%
  mutate(n = dt$n[which(dt$variable == "inlake_slope")])

knitr::kable(dt, digits = 0, format = "markdown") 
```
